---
title: A title
subtitle: A subtitle
format:
  clean-revealjs:
    echo: true
html-math-method:
  method: mathjax
  url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
author:
  - name: Brenton Kenkel
    email: brenton.kenkel@gmail.com
    affiliations: Vanderbilt University
date: last-modified
---

## Example slide

### This is a subtitle

Here we have some text that may run over several lines of the slide frame,
depending on how long it is.

- first item 
    - A sub item

Next, we'll brief review some theme-specific components.

- Note that _all_ of the standard Reveal.js
[features](https://quarto.org/docs/presentations/revealjs/)
can be used with this theme, even if we don't highlight them here.

## Additional theme classes

### Some extra things you can do with the clean theme

Special classes for emphasis

- `.alert` class for default emphasis, e.g. [important note]{.alert}.
- `.fg` class for custom colour, e.g. [important note]{.fg style="--col: #e64173"}.
- `.bg` class for custom background, e.g. [important note]{.bg style="--col: #e64173"}.

Cross-references

- `.button` class provides a Beamer-like button, e.g.
[[Summary]{.button}](#sec-summary)

Block environments

:::{.example}
The `.example` class marks off worked examples like this one.
:::

## Math

### Inline and display math should match the text face

Let $\hat\beta = (X'X)^{-1}X'y$ denote the least-squares estimator.

Under the usual assumptions, we have

$$
\begin{aligned}
\mathbb{E}[\hat\beta \mid X] &= \beta, \\
\mathbb{V}[\hat\beta \mid X] &= \sigma^2 (X'X)^{-1}.
\end{aligned}
$$

The estimator is consistent: $\hat\beta \overset{p}{\to} \beta$ as $n \to \infty$.

## Tables

### Check digit alignment and hairline rules

| Country | Year | GDP per capita | Growth  |
|---------|------|---------------:|--------:|
| France  | 1820 |          1,135 |   0.84% |
| France  | 1870 |          1,876 |   1.01% |
| Prussia | 1820 |          1,077 |   0.61% |
| Prussia | 1870 |          1,839 |   1.08% |
| UK      | 1820 |          1,706 |   0.51% |
| UK      | 1870 |          3,190 |   1.26% |

: Made-up numbers in the style of Maddison {.striped-off}

## Figures

```{r}
#| echo: false
#| message: false
#| fig-cap: "A ggplot figure with a caption."
#| fig-width: 7
#| fig-height: 3.5
library("ggplot2")
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
  labs(x = "Weight (1000 lbs)", y = "Miles per gallon")
```

## Summary {#sec-summary}

### A minimalist theme for academic slides

This is `quarto-revealjs-bjk`, Brenton Kenkel's fork of Grant McDermott's [clean theme](https://github.com/grantmcdermott/quarto-revealjs-clean).

Add the theme to an existing project.

```{.bash}
quarto install extension brentonk/quarto-revealjs-bjk
```

... or, create a new project using this slide deck as a template.

```{.bash}
quarto use template brentonk/quarto-revealjs-bjk
```

## R code

```{r}
#| echo: true
#| eval: false
library("tidyverse")
df_test <- read_csv("~/dir/test.csv")

df_test |>
  mutate(var = case_when(
           var < 0 ~ "negative",
           var != 0 ~ "positive",  # checking that ligatures disabled
           TRUE ~ "zero"
         ))

## Can go 93 chars without wrapping
--------10--------20--------30--------40--------50--------60--------70--------80--------90---
```

## R code with output

Here's some code and output

```{r}
getwd()
```

Let's check the spacing afterward too

:::{.callout-note}
## I'm a callout note!

Isn't that cool?
:::
